Symmetric Peer-to-Peer Applications

### 2022-09-04 tpd-22.tex
...

In this section, we evaluate if our design meets its goals to ensure that all
peers (a) meet event deadlines, (b) advance in sync in real time, and (c) can
leave and join the network and remain symmetric.
%
For each of these goals, we simulate different network scenarios varying the
(i) topology, (j) latency, (k) churn, and (k) frequency and (m) deadlines of
events.
For each scenario, we measure (x) the recurrence of time travels, (y) the
real-time pace of peers, and (z) the correctness of unstable peers, such that
they validate goals (a), (b), and (c), respectively.

@@

\section{TODO}

>>>>

In this section, we evaluate if our design meets its goals to ensure that all
peers (a) meet event deadlines, (b) advance in sync in real time, and (c) can
leave and join the network and remain symmetric.
%
We simulate an application varying the network topology, latency, and churn, as
well as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the correctness of unstable peers, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We can count all time travel occurrences during the simulation.
%
Regarding (b), we can use an absolute simulation clock to track, in real time,
the pace of each peer in comparison to a reference peer most advanced in time.
%
Regarding (c), we can TODO specific peers and very that they TODO within a
short period of time.

For instance, if the reference peer signals $T$ and then a peer signals $T-dt$,
than we.
That would be the case when a source peer generates an event with a small
deadline in comparison to the latency to the farthest destination peer.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{topo}
  \caption{
    \label{fig.topo}
    TODO
  }
\end{figure*}

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with straight lines, long cycles, and short cycles.
%
In order to have an absolute clock to compare peers, we use a single machine
to simulate all peers, and output their logs to a single file.
We TODO the network latency and clock skew using TODO and TODO.

We now detail why we measure the properties above and how we instrument the
middleware implementation:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
We teak the middleware implementation to count time travel ticks.
We then measure the percentage of the sum of all time travels ticks over the to
the total simulation ticks (e.g., $1\%$, if all peers sum $1000$ time travel
ticks over $100k$ accumulated simulation ticks).
%
\item \textbf{Real-time pace of peers:}
We start each peer with a random delay of up to $10s$ to force a time mismatch,
and then verify if they synchronize and remain synchronized during the whole
simulation.
We teak the middleware to output its current tick every $100ms$.

More concretely, we measure the percentage o ticks diverging from the reference
peer (e.g., $1\%$, if .

%
\end{enumerate}

We run the simulation for 5 minutes and, since we start the measures after 1 minute

@@

-- use of space for snapshots
-    - limit to go back?
-    - super nodes? (when connecting, pass tick, may close if tick<last)

-- start with random deltas
\section{TODO}
